Demystifying the Computer Science Ph.D. Admission in the US

### 2023-06-06 phd-cs-us.tex
updates

\section{Acknowledgement}

The following people contributed to this document: Craig Yu (GMU), Hakan Aydin (GMU).

\bibliographystyle{abbrv}
\bibliography{phd-cs-us.bib}
\newpage

@@

** Current 2023 Rankings of CS PhD programs in the U.S.
  Below is the 2023 Rankings from [[https://www.csrankings.org][CSRankings.org]] as of <2023-04-09 Sun>.

1. Carnegie Mellon University 
2. Univ. of Illinois at Urbana-Champaign 
3. Univ. of California - San Diego  
4. Massachusetts Institute of Technology 
5. Stanford University 
5. University of Michigan  
7. University of Washington 
8. Cornell University  
8. Univ. of California - Berkeley  
10. Georgia Institute of Technology 
11. Northeastern University  
11. University of Maryland - College Park 
13. University of Wisconsin - Madison  
14. Purdue University  closed chart
15. University of Texas at Austin  
16. Columbia University  
16. University of Pennsylvania 
18. New York University  
18. Princeton University 
20. University of Massachusetts Amherst  
21. Univ. of California - Los Angeles
22. University of Chicago 
23. Stony Brook University
23. Univ. of California - Santa Barbara 
25. Rutgers University  
26. Univ. of California - Irvine 
27. University of Southern California 
28. Duke University 
29. Univ. of California - Riverside
30. Pennsylvania State University 
31. Northwestern University 
32. Ohio State University 
33. George Mason University 
33. Harvard University  
35. Brown University  
35. University of Utah 
37. Texas A&M University
37. Univ. of California - Santa Cruz  
37. Yale University  
40. Boston University 
40. University at Buffalo
40. University of Colorado Boulder 
43. North Carolina State University
44. Rice University 
44. University of Illinois at Chicago  
46. University of North Carolina 
46. University of Virginia 
48. Arizona State University 
48. University of Minnesota 
48. Virginia Tech  
51. Oregon State University  
51. Univ. of California - Davis

>>>>

\subsection{Current 2023 Rankings of CS PhD programs in the U.S}
  Below is the 2023 Rankings from \href{https://www.csrankings.org}{CSRankings.org}, a ranking system that is based on top CS conferences, as of April 2023.

\begin{itemize}
\item Carnegie Mellon University 
\item Univ. of Illinois at Urbana-Champaign 
\item Univ. of California - San Diego  
\item Massachusetts Institute of Technology 
\item Stanford University         
\item University of Michigan  
\item University of Washington 
\item Cornell University  
\item Univ. of California - Berkeley  
\item Georgia Institute of Technology 
\item Northeastern University  
\item University of Maryland - College Park 
\item University of Wisconsin - Madison  
\item Purdue University  closed chart
\item University of Texas at Austin  
\item Columbia University  
\item University of Pennsylvania 
\item New York University  
\item Princeton University 
\item University of Massachusetts Amherst  
\item Univ. of California - Los Angeles
\item University of Chicago 
\item Stony Brook University
\item Univ. of California - Santa Barbara 
\item Rutgers University  
\item Univ. of California - Irvine 
\item University of Southern California 
\item Duke University 
\item Univ. of California - Riverside
\item Pennsylvania State University 
\item Northwestern University 
\item Ohio State University 
\item George Mason University 
\item Harvard University  
\item Brown University  
\item University of Utah 
\item Texas A\&M University
\item Univ. of California - Santa Cruz  
\item Yale University  
\item Boston University 
\item University at Buffalo
\item University of Colorado Boulder 
\item North Carolina State University
\item Rice University 
\item University of Illinois at Chicago  
\item University of North Carolina 
\item University of Virginia 
\item Arizona State University 
\item University of Minnesota 
\item Virginia Tech  
\item  Oregon State University  
\item Univ. of California - Davis
\end{itemize}

\section{Acknowledgement}
Many faculty and students have contributed to this document.
Craig Yu (GMU) and Hakan Aydin (GMU) contributed to the early version of this document. Other GMU faculty also have provided valuable feedbacks.  Thanks to all of them.
\bibliographystyle{abbrv}
\bibliography{phd-cs-us.bib}
\newpage

@@
